Empirical Option Returns and the risk-free Rate in Crypto Asset Markets

### 2024-02-20 written/paper.tex
more table links

We refer to the QQ plots of the daily returns of the zero-beta portfolios versus the t-distribution to conclude that the returns are in fact t-distributed (Figure 5 and Figure 6). We conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
The null hypothesis is rejected on a high significance level for ATM and slightly ITM options. 
In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table 7 and Table 8).
The results hold across model variations, vanilla and crash resistant, with or without fees (Figure 7-14).

>>>>

We refer to the QQ plots of the daily returns of the zero-beta portfolios versus the t-distribution to conclude that the returns are in fact t-distributed (Figure 5 and Figure 6). We conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
The null hypothesis is rejected on a high significance level for ATM and slightly ITM options. 
In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table~\ref{table:btc_t_stats} and ~\ref{table:eth_t_stats}).
The results hold across model variations, vanilla and crash resistant, with or without fees (Figure 7-14).
